---
title: "mod viz"
data: "2026-05-10"
---

# preamble and loading

```{r pathfinding}
here::i_am("scripts/analysis-viz.Rmd")
```

```{r load libs and utils}
library(here)
library(tidyverse)
library(patchwork) # for plot_layout
# 
# library(survival) # for fitting surv objects
# library(survminer) # for plotting surv ojects

source(here("scripts/wrangle.R"))
source(here("scripts/viz_utils.R"))
```

```{r load data}
# data
source(here("scripts/R/tidy.R"))

dfs_tidy <- dfs_tidy %>%
  lapply(., \(x){
    x %>% 
      mutate(across(starts_with("trt"), as.factor))
  }
  )
```

# development

## plot fns

```{r}
# plot development variants
PlotDevVars <- function(x){
  x %>%
    ggplot(aes(#shape = trt.maxT, fill = trt.flucT,
               fill = trt.maxT, shape = trt.flucT,
               lty = trt.flucT, #color = trt.meanT,
               group = trt.flucT,)) +
    geom_point(size = 2) +
    #geom_line() +
    # geom_errorbar(aes(ymax = avg.exit + se.exit,
    #                 ymin = avg.exit - se.exit),
    #               width = 0.25, lty = "solid", show.legend = FALSE) +
    # geom_text(aes(label = n),
    #           vjust = -0.2, hjust = -0.3,
    #           show.legend = FALSE) +
    
    ### if fill = maxT, shape = flucT ###
    scale_shape_manual(values = c(`3.5` = 21, `7` = 24)) +
    scale_fill_manual(values = c(`33` = "white", `40` = "black")) +
    guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
           fill = guide_legend(override.aes = list(shape = c(1, 16)))) +
    labs(fill = "max temp", shape = "fluct temp",
    ) +
    ###
    
    # ### if shape = maxT, fill = flucT ###
    # scale_shape_manual(values = c(`33` = 21, `40` = 24)) +
    # scale_fill_manual(values = c(`3.5` = "white", `7` = "black")) +
    # guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
    #        fill = guide_legend(override.aes = list(shape = c(1, 16)))) +
    # #scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
    # labs(#lty = "fluctuation (°C)",
    #      shape = "max temp",
    #      fill = "fluct temp",
    #     # color = "mean temp"
    # ) +
    # ###
    
    theme_bw()
}
```


## prop survival
```{r}
# first attempt...
dfs_tidy$wide %>%
  CalcSurvSS() %>%
  ggplot(aes(y = prop.pup, x = trt.maxT,
             shape = trt.meanT, lty = trt.flucT,
             group = trt.flucT)) +
  geom_point(size = 2) +
  geom_line() +
  geom_errorbar(aes(ymax = prop.pup + se.pup,
                    ymin = prop.pup - se.pup),
                width = 0.25, lty = "solid", show.legend = FALSE) +
  geom_text(aes(label = n),
            vjust = -0.2, hjust = -0.3) +
  theme_bw() +
  labs(y = "proportion survived",
       x = "max temperature (°C)",
       lty = "fluctuation (°C)",
       shape = "mean temperature (°C)")
```

```{r}
# try to visualise w different axes...
df <- dfs_tidy$wide %>%
  CalcSurvSS()

.plotfn <- function(x){
  x %>%
    ggplot(aes(y = prop, 
               fill = trt.maxT, shape = trt.flucT,
               lty = trt.flucT, #color = trt.meanT,
               group = trt.flucT,)) +
    geom_point(size = 2) +
    #geom_line() +
    geom_errorbar(aes(ymax = prop.pup + se.pup,
                      ymin = prop.pup - se.pup),
                  width = 0.25, lty = "solid", show.legend = FALSE) +
    geom_text(aes(label = n),
              vjust = -0.2, hjust = -0.3,
              show.legend = FALSE) +
    scale_shape_manual(values = c(`3.5` = 21, `7` = 24)) +
    scale_fill_manual(values = c(`33` = "white", `40` = "black")) +
    guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
           fill = guide_legend(override.aes = list(shape = c(1, 16)))) +
    #scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
    labs(y = "proportion survived",
         #lty = "fluctuation (°C)",
         shape = "fluct temp",
         fill = "max temp",
        # color = "mean temp"
    ) +
    theme_bw()
}

p <- list(
  p1 = df %>%
    .plotfn() +
    aes(x = trt.maxT) +
    labs(x = "max temp (°C)"),
  
  p2 = df %>%
    .plotfn() +
    aes(x = trt.minT) +
    labs(x = "min temp (°C)"),
  
  
  p3 = df %>%
    .plotfn() +
    aes(x = trt.meanT) +
    labs(x = "mean temp (°C)")
)

p$p1 + p$p2 + p$p3 +
  plot_layout(axes = "collect", guides = "collect",
              widths = c(1, 1.5, 2)) &
  theme(legend.position = "bottom")

```



## dev trajectories

```{r}
# plots avgs; incls pmds
df <- dfs_tidy$long %>%
  filter(#is.sup != 1 # or just NA this column if dgaf
         ) %>%
  group_by(is.sup) %>%
  CalcDevSS() %>%
  filter(trt.type == "dev",
         instar != "LPI",
         !is.na(is.sup) # is.na(is.sup) = things that died < 5
         ) %>%
  mutate(instar = factor(instar, levels = c("pmd", "hatch", "2nd", "3rd", "4th", "5th", "6th", "wander", "pupa", "eclose"))) %>%
  filter(!(instar %in% c("hatch", "pmd", "2nd")))

.plotfn <- function(x){
  x %>%
    filter(!(instar %in% c("wander", "pupa", "eclose"))) %>%
    ggplot(aes(#col = trt.maxT, 
               col = trt.meanT,
               lty = trt.flucT,
             group = interaction(trt.meanT, trt.flucT))) +
    geom_point(#aes(alpha = n),
               size = 2.5) +
  geom_line() +
  scale_color_hue(direction = -1) +
  theme_bw() +
    facet_wrap(~is.sup, labeller = as_labeller(c(`0` = "non-supernumerary",
                                                 `1` = "supernumerary")),
               scales = "free_x") +
    labs(lty = "fluctuation", col = "mean temp") +
    scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE))
}

# dev trajectory
df %>%
  .plotfn() +
  aes(y = avg.logmass, x = avg.tt,
      shape = instar) +
  geom_errorbar(aes(ymax = avg.logmass + se.logmass,
                    ymin = avg.logmass - se.logmass),
                width = 0.2, lty = "solid", show.legend = FALSE) +
  geom_errorbarh(aes(xmax = avg.tt + se.tt,
                     xmin = avg.tt - se.tt),
                 height = 0.1, lty = "solid", show.legend = FALSE) +
  labs(y = "ln mass", x = "time to instar (days)",
       shape= "instar")


# mass vs instar
df %>%
  .plotfn() +
  aes(y = avg.logmass, x = instar,
      shape = trt.maxT) +
  geom_errorbar(aes(ymax = avg.logmass + se.logmass,
                    ymin = avg.logmass - se.logmass),
                width = 0.1, lty = "solid", show.legend = FALSE) +
    labs(y = "ln mass", x = "instar",
       shape= "max temp")

# development rate vs instar
df %>%
  .plotfn() +
  aes(y = avg.tt, x = instar,
      shape = trt.maxT) +
  geom_errorbar(aes(ymax = avg.tt + se.tt,
                    ymin = avg.tt - se.tt),
                width = 0.1, lty = "solid", show.legend = FALSE) +
  labs(y = "time (days)", x = "instar", shape = "max temp")
```

```{r}
# plot individs; incls pmds
df <- dfs_tidy$long %>%
  filter(trt.type == "dev") %>%
  mutate(logmass = log(mass)) %>%
  # group_by(across(c(starts_with("trt"), "instar"))) %>%
  # summarise(n = n(),
  #           across(.cols = c(mass, logmass, tt),
  #                  .fns = list(avg = ~ mean(.x, na.rm = TRUE),
  #                              se = se),
  #                  .names = "{.fn}.{.col}")) %>%
  #   ungroup() %>%
  mutate(instar = factor(instar, levels = c("hatch", "2nd", "3rd", "4th", "5th", "6th", "wander", "LPI", "pupa", "eclose", "pmd")),
         is.sup = case_when(is.na(is.sup) ~ 2,
                            TRUE ~ is.sup)
         ) %>%
  filter(!(instar %in% c("hatch", "2nd", "eclose", "pupa", "LPI",
                         "pmd" # no mass so doesnt matter
                         )),
         !is.na(tt))

# all fates
df %>%
  #filter(is.pup == 0) %>%
  ggplot(aes(y = logmass, x = tt,
             shape = instar,
             group = id,
             color = as.factor(is.pup),
             lty = as.factor(is.sup)
             )) +
  geom_point(alpha = 0.75) +
  geom_line(alpha = 0.75) +
  #facet_grid(trt ~ cohort) +
  facet_wrap(~ trt, #scales = "free_x",
            labeller = as_labeller(c(`319` = "33-19°C (26±7)", `326` = "33-26°C (29.5±3.5)",
                                     `426` = "40-26°C (33±7)", `433` = "40-33°C (36.5±3.5)"))) +
  scale_shape_manual(values = c("3rd" = 16, "4th" = 17, "5th" = 15, "6th" = 10,
                                "wander" = 3, "pupa" = 8, "LPI" = 8, "pmd" = 4),
                     labels = c("3rd" = "3rd", "4th" = "4th", "5th" = "5th", "6th" = "6th", 
                                "wander" = "wander", "pupa" = "pupa", "LPI" = "LPI", 
                                "pmd" = "died as larva")) +
  scale_color_manual(values = c(`0` = "gray", `1` = "green3", `2` = "orange1"),
                     labels = c(`0` = "died as larva", `1` = "pupated", `2` = "LPI")) +
  scale_linetype_manual(values = c(`0` = "solid", `1` = "dashed", `2` = "dotted"),
                        labels = c(`0` = "non-sup (wandered after 5 instars)", `1` ="supernumerary (6+ instars)",
                                   `2` = "died within 5 instars")) +
  guides(shape = guide_legend(order = 1, #nrow = 2, byrow = TRUE
                              ),
         col = guide_legend(order = 2, #nrow = 1, byrow = TRUE
                            ),
         lty = guide_legend(order = 3, #nrow = 2, byrow = TRUE
                            )) +
  theme_bw() +
  theme(#legend.position = "bottom",
        legend.box = "vertical",
        legend.margin = margin()) +
  labs(y = "log[mass]",
       x = "days",
       col = "fate",
       lty = "supernumerary?")

## by instar of death
dfs_tidy$wide %>%
  filter(trt.type == "dev") %>%
  mutate(last.stage = case_when(!is.na(jdate.pupa) | !is.na(jdate.LPI) ~ "pupa",
                                !is.na(jdate.wander) ~ "wander",
                                !is.na(jdate.6th) ~ "6th",
                                !is.na(jdate.5th) ~ "5th",
                                !is.na(jdate.4th) ~ "4th",
                                !is.na(jdate.3rd) ~ "3rd"),
         tt.last = case_when(!is.na(jdate.pupa) ~ jdate.pupa,
                             !is.na(jdate.LPI) ~ jdate.LPI,
                                    last.stage == "wander" ~ jdate.wander,
                                    last.stage == "6th" ~ jdate.6th,
                                    last.stage == "5th" ~ jdate.5th,
                                    last.stage == "4th" ~ jdate.4th,
                                    last.stage == "3rd" ~ jdate.3rd),
         tt.last = tt.last - jdate.hatch,
         last.stage = factor(last.stage, levels = c("3rd", "4th", "5th", "6th", "wander", "pupa")),
         is.sup = case_when(is.na(is.sup) ~ 2,
                            TRUE ~ is.sup)
         ) %>%
  pivot_longer(cols = starts_with(c("jdate", "mass", "tt")),
                 names_to = c(".value", "instar"),
                 values_drop_na = TRUE,
                 names_pattern = ("([a-z]*\\d*)\\.(\\d*[a-z|A-Z]*)")) %>%
  filter(instar == "last") %>% #View()
  #filter(last.stage != "pupated") %>%
  ggplot(aes(y = last.stage, x = tt,
             shape = as.factor(is.sup),
             group = id,
             #color = last.stage,
             col = as.factor(is.pup)
             )) +
  geom_point(alpha = 0.95) +
  geom_line(alpha = 0.95) +
  #facet_grid(trt ~ cohort) +
  facet_wrap(~ trt, #scales = "free_x",
             labeller = as_labeller(c(`319` = "33-19°C (26±7)", `326` = "33-26°C (29.5±3.5)",
                                      `426` = "40-26°C (33±7)", `433` = "40-33°C (36.5±3.5)"))) +
  scale_color_manual(values = c(`0` = "gray", `1` = "green3", `2` = "orange1"),
                     labels = c(`0` = "died as larva", `1` = "pupated", `2` = "LP intermediate"),
                     breaks = c(1, 2, 0)) +
  scale_shape_manual(values = c(`0` = 16, `1` = 1, `2` = 4),
                     labels = c(`0` = "5 larval instars", 
                                `1` ="6+ larval instars",
                                `2` = "died within 5 instars"),
                     breaks = c(0, 1, 2)) +
  theme_bw() +
  theme(#legend.position = "bottom",
    legend.box = "vertical",
    legend.margin = margin()) +
  labs(y = "final instar",
       x = "days from hatching",
       shape = "instars before wandering?",
       col = "pupation success?")
```

## mass at

```{r}
df <- dfs_tidy$long %>%
  #filter(trt.type == "dev") %>%
  CalcDevSS() %>%
  filter(instar %in% c("5th", "pupa", "eclose")) %>%
  mutate(instar = factor(instar, levels = c("5th", "pupa", "eclose")))

.plotfn <- function(x){
  x %>% PlotDevVars() +
  list(
    aes(y = avg.mass),
    geom_errorbar(aes(ymax = avg.mass + se.mass,
                      ymin = avg.mass - se.mass),
                  width = 0.5, lty = "solid", show.legend = FALSE),
    labs(y = "mass"),
    facet_grid(instar ~ ., scales = "free_y")
  )
}


p <- list(
  p1 = df %>%
    .plotfn() +
    aes(x = trt.maxT) +
    labs(x = "max temp (°C)") +
    theme(strip.background = element_blank(),
          strip.text = element_blank()),
  
  p2 = df %>%
    .plotfn() +
    aes(x = trt.minT) +
    labs(x = "min temp (°C)") +
    theme(strip.background = element_blank(),
          strip.text = element_blank(),
          axis.title.y = element_blank()),
  
  
  p3 = df %>%
    .plotfn() +
    aes(x = trt.meanT) +
    labs(x = "mean temp (°C)") +
    theme(axis.title.y = element_blank())
)

p$p1 + p$p2 + p$p3 +
  plot_layout(axes = "collect", guides = "collect",
              widths = c(1, 1.5, 2)) &
  theme(legend.position = "bottom")
```

## time to instar
```{r}
df <- dfs_tidy$long %>%
  #filter(trt.type == "dev") %>%
  CalcDevSS() %>%
  filter(instar %in% c("5th", "pupa", "eclose")) %>%
  mutate(instar = factor(instar, levels = c("5th", "pupa", "eclose")))

.plotfn <- function(x){
  x %>% PlotDevVars() +
  list(
    aes(y = avg.tt),
    geom_errorbar(aes(ymax = avg.tt + se.tt,
                      ymin = avg.tt - se.tt),
                  width = 0.5, lty = "solid", show.legend = FALSE),
    labs(y = "duration (days)"),
    facet_grid(instar ~ ., scales = "free_y")
  )
}

p <- list(
  p1 = df %>%
    .plotfn() +
    aes(x = trt.maxT) +
    labs(x = "max temp (°C)") +
    theme(strip.background = element_blank(),
          strip.text = element_blank()),
  
  p2 = df %>%
    .plotfn() +
    aes(x = trt.minT) +
    labs(x = "min temp (°C)") +
    theme(strip.background = element_blank(),
          strip.text = element_blank(),
          axis.title.y = element_blank()),
  
  
  p3 = df %>%
    .plotfn() +
    aes(x = trt.meanT) +
    labs(x = "mean temp (°C)") +
    theme(axis.title.y = element_blank())
)

p$p1 + p$p2 + p$p3 +
  plot_layout(axes = "collect", guides = "collect",
              widths = c(1, 1.5, 2)) &
  theme(legend.position = "bottom")
```
```



# tdt stuff

```{r}
# df prep
df <- dfs_tidy$wide %>%
  CalcTDTSS()
```

## combined mass/time
```{r}
df %>%
  filter(instar == "24h") %>%
  ggplot(aes(x = avg.dmass, y = avg.exit,
             #lty = cohort,
             col = trt.maxT, shape = trt.flucT)) +
  geom_point(size = 2) +
  geom_line() +
  geom_errorbar(aes(ymax = avg.exit + se.exit,
                    ymin = avg.exit - se.exit),
                width = 5) +
  # geom_errorbarh(aes(xmax = avg.dmass + se.dmass,
  #                    xmin = avg.dmass - se.dmass)) +
  scale_color_hue(direction = -1) +
  theme_bw() +
  labs(y = "days survived after transferring",
       x = "mass diff. 24h after transferring",
       col = p_scales$lab_maxT,
       shape = p_scales$lab_flucT)
```

## exit time
```{r}
# one fig
df %>%
  #filter(instar == "24h") %>%
  ggplot(aes(y = avg.exit, x = trt.maxT,
             #x = trt.meanT, shape = trt.maxT,
             #col = trt.flucT, 
              group = interaction(trt.flucT),
             )) +
  #facet_wrap(~cohort) +
  geom_line(aes(lty = trt.flucT,)) +
  geom_errorbar(aes(ymax = avg.exit + se.exit,
                    ymin = avg.exit - se.exit),
                width = 0.25, lty = "solid", show.legend = FALSE
                ) +
  geom_point(aes(col = trt.meanT, 
                 shape = trt.meanT),
             size = 2.5) +
  #scale_color_hue(direction = -1) +
  #scale_color_brewer(palette = "Reds") +
   scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
  theme_bw() +
  labs(y = "days survived after transfer to 40°C",
       x = "maximum temperature (°C)",
       #col = p_scales$lab_flucT,
       col = "mean temp",
       shape = "mean temperature (°C)",
       lty = p_scales$lab_flucT)
```

```{r}
.plotfn <- function(x){
  x %>%
    filter(trt.type == "tdt",
           instar == "0h" # drop dups
           ) %>%
    ggplot(aes(y = avg.exit, 
               fill = trt.maxT, shape = trt.flucT,
               lty = trt.flucT, #color = trt.meanT,
               group = trt.flucT,)) +
    geom_point(size = 2) +
    #geom_line() +
    geom_errorbar(aes(ymax = avg.exit + se.exit,
                    ymin = avg.exit - se.exit),
                  width = 0.25, lty = "solid", show.legend = FALSE) +
    geom_text(aes(label = n),
              vjust = -0.2, hjust = -0.3,
              show.legend = FALSE) +
    scale_shape_manual(values = c(`3.5` = 21, `7` = 24)) +
    scale_fill_manual(values = c(`33` = "white", `40` = "black")) +
    guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
           fill = guide_legend(override.aes = list(shape = c(1, 16)))) +
    #scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
    labs(y = "days to exit (from transfer)",
         #lty = "fluctuation (°C)",
         fill = "max temp",
         shape = "fluct temp",
        # color = "mean temp"
    ) +
    theme_bw()
}

p <- list(
  p1 = df %>%
    .plotfn() +
    aes(x = trt.maxT) +
    labs(x = "max temp (°C)"),
  
  p2 = df %>%
    .plotfn() +
    aes(x = trt.minT) +
    labs(x = "min temp (°C)"),
  
  
  p3 = df %>%
    .plotfn() +
    aes(x = trt.meanT) +
    labs(x = "mean temp (°C)")
)

p$p1 + p$p2 + p$p3 +
  plot_layout(axes = "collect", guides = "collect",
              widths = c(1, 1.5, 2)) &
  theme(legend.position = "bottom")
```



## mass change

```{r}
.plotfn <- function(x){
  x %>%
    filter(instar != "0h") %>%
    ggplot(aes(x = trt.maxT,
               #x = trt.meanT, shape = trt.maxT,
               col = trt.flucT, lty = trt.flucT, #shape = trt.flucT,
               shape = trt.meanT,
               group = trt.flucT)) +
    geom_point(size = 2) +
    geom_line() +
    #facet_wrap(~cohort) +
    scale_color_hue(direction = -1) +
    theme_bw() +
    labs(x = "maximum temperature (°C)",
         col = p_scales$lab_flucT,
         lty = p_scales$lab_flucT,
         shape = "mean temperature (°C)"
         #shape = p_scales$lab_flucT
    ) +
    guides(shape = guide_legend(override.aes = list(color = c("#F8766D", "#00BFC4", "#F8766D", "#00BFC4"))))
}

# 2x2 by transfer day
df %>%
  .plotfn() +
  aes(y = avg.dmass) +
  geom_errorbar(aes(ymax = avg.dmass + se.dmass,
                    ymin = avg.dmass - se.dmass),
                width = 0.25, lty = "solid", show.legend = FALSE
  ) +
  facet_wrap(~instar, labeller = as_labeller(c(`24h` =  "24h after transfer to 40°C",
                                               `48h` =  "48h after transfer to 40°C"))) +
  labs(y = "mass difference (mg)")
  


df %>%
  .plotfn() +
  aes(y = avg.rmass) +
  geom_errorbar(aes(ymax = avg.rmass + se.rmass,
                    ymin = avg.rmass - se.rmass),
                width = 0.25, lty = "solid", show.legend = FALSE
                ) +
  facet_wrap(~instar, labeller = as_labeller(c(`24h` =  "24h:0h after transfer to 40°C",
                                               `48h` =  "48h:24h after transfer to 40°C"))) +
  labs(y = "mass ratio")
```

```{r}
.plotfn <- function(x){
  x %>%
    filter(instar %in% c("24h", "48h")) %>%
    ggplot(aes(x = instar,
               #shape = trt.maxT, 
               shape = trt.meanT,
               col = trt.maxT, 
               lty = trt.flucT, 
               group = interaction(trt.flucT, trt.maxT))) +
    geom_point(size = 2) +
    geom_line() +
    scale_color_hue(direction = -1) +
    theme_bw() +
    labs(#col = "fluctuation", lty = "fluctuation",
      #shape = "max temp",
      #shape = p_scales$lab_maxT,
      shape = "mean temperature (°C)",
      col = p_scales$lab_maxT,
      lty = p_scales$lab_flucT
    )
}

# 0:24 vs 24:48
df %>%
  .plotfn() +
  aes(y = avg.dmass) +
  geom_errorbar(aes(ymax = avg.dmass + se.dmass,
                    ymin = avg.dmass - se.dmass),
                width = 0.25, lty = "solid", show.legend = FALSE
                ) +
  labs(y = "change in mass (mg)",
       x = "h after transfer to 40°C",)

df %>%
  .plotfn() +
  aes(y = avg.rmass) +
  geom_errorbar(aes(ymax = avg.rmass + se.rmass,
                    ymin = avg.rmass - se.rmass),
                width = 0.25, lty = "solid", show.legend = FALSE
                )
```


## dev trajectory

```{r}
## individuals
dfs_tidy$wide %>%
  filter(trt.type == "tdt") %>% 
  # stdise times
  mutate(tt.0h = 0,
         tt.24h = 1,
         tt.48h = 2) %>%
  select(c("cohort", "id", starts_with("trt"), contains(c("pmd", "0h", "24h", "48h")))) %>%
  pivot_longer(cols = ends_with(c("0h", "24h", "48h")),
               names_to = c(".value", "instar"),
               names_sep = "\\.") %>%
  mutate(instar = factor(instar, levels = c("0h", "24h", "48h", "pmd"))) %>%
  ggplot(aes(y = mass, x = tt, 
             shape = instar,
             group = id,
             col = tt.pmd),
         ) +
  geom_point() +
  geom_line() +
  facet_wrap(~trt) +
  scale_color_viridis_c(option = "Plasma") +
  labs(x = "days from transfer")


## avg
dfs_tidy$wide %>%
  CalcTDTSS() %>%
  ggplot(aes(y = avg.mass, x = instar,
               fill = trt.maxT, shape = trt.flucT,
               lty = trt.flucT, #color = trt.meanT,
               group = interaction(trt.flucT, trt.maxT))) +
    geom_point(size = 2) +
    geom_line() +
    geom_errorbar(aes(ymax = avg.mass + se.mass,
                    ymin = avg.mass - se.mass),
                  width = 0.25, lty = "solid", show.legend = FALSE) +
    # geom_text(aes(label = n),
    #           vjust = -0.2, hjust = -0.3,
    #           show.legend = FALSE) +
    scale_shape_manual(values = c(`3.5` = 21, `7` = 24)) +
    scale_fill_manual(values = c(`33` = "white", `40` = "black"),
                      ) +
  scale_linetype_manual(values = c(`3.5` = "solid", `7` = "dashed")) +
    guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
           fill = guide_legend(override.aes = list(shape = c(1, 16),
                                                   linetype = c("solid", "3223")))) +
    #scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
    labs(#y = "days to exit (from transfer)",
         lty = "fluct temp",
         fill = "max temp",
         shape = "fluct temp",
        # color = "mean temp"
    ) +
  #facet_wrap(~instar) +
    theme_bw() +
  labs(x = "hrs after transfer to 40C",
       y = "mass")
```
