---
title: "mod viz"
data: "2026-05-10"
---

# preamble and loading

```{r pathfinding}
here::i_am("scripts/analysis-viz.Rmd")
```

```{r load libs and utils}
library(here)
library(tidyverse)
library(patchwork) # for plot_layout
# 
# library(survival) # for fitting surv objects
# library(survminer) # for plotting surv ojects

source(here("scripts/wrangle.R"))
source(here("scripts/viz_utils.R"))
```

```{r load data}
# data
source(here("scripts/R/tidy.R"))

dfs_tidy <- dfs_tidy %>%
  lapply(., \(x){
    x %>% 
      mutate(across(starts_with("trt"), as.factor))
  }
  )
```

# development

## plot fns

```{r}
# plot development variants
PlotDevVars <- function(x){
  x %>%
    ggplot(aes(shape = trt.maxT, fill = trt.flucT,
               lty = trt.flucT, #color = trt.meanT,
               group = trt.flucT,)) +
    geom_point(size = 2) +
    #geom_line() +
    # geom_errorbar(aes(ymax = avg.exit + se.exit,
    #                 ymin = avg.exit - se.exit),
    #               width = 0.25, lty = "solid", show.legend = FALSE) +
    # geom_text(aes(label = n),
    #           vjust = -0.2, hjust = -0.3,
    #           show.legend = FALSE) +
    scale_shape_manual(values = c(`33` = 21, `40` = 24)) +
    scale_fill_manual(values = c(`3.5` = "white", `7` = "black")) +
    guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
           fill = guide_legend(override.aes = list(shape = c(1, 16)))) +
    #scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
    labs(#lty = "fluctuation (°C)",
         shape = "max temp",
         fill = "fluct temp",
        # color = "mean temp"
    ) +
    theme_bw()
}
```

## survival
```{r}
# try to visualise w different axes...
df <- dfs_tidy$wide %>%
  CalcSurvSS()

.plotfn <- function(x){
  x %>%
    ggplot(aes(y = prop.pup, 
               shape = trt.maxT, fill = trt.flucT,
               lty = trt.flucT, #color = trt.meanT,
               group = trt.flucT,)) +
    geom_point(size = 2) +
    #geom_line() +
    geom_errorbar(aes(ymax = prop.pup + se.pup,
                      ymin = prop.pup - se.pup),
                  width = 0.25, lty = "solid", show.legend = FALSE) +
    geom_text(aes(label = n),
              vjust = -0.2, hjust = -0.3,
              show.legend = FALSE) +
    scale_shape_manual(values = c(`33` = 21, `40` = 24)) +
    scale_fill_manual(values = c(`3.5` = "white", `7` = "black")) +
    guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
           fill = guide_legend(override.aes = list(shape = c(1, 16)))) +
    #scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
    labs(y = "proportion survived",
         #lty = "fluctuation (°C)",
         shape = "max temp",
         fill = "fluct temp",
        # color = "mean temp"
    ) +
    theme_bw()
}

p <- list(
  p1 = df %>%
    .plotfn() +
    aes(x = trt.maxT) +
    labs(x = "max temp (°C)"),
  
  p2 = df %>%
    .plotfn() +
    aes(x = trt.minT) +
    labs(x = "min temp (°C)"),
  
  
  p3 = df %>%
    .plotfn() +
    aes(x = trt.meanT) +
    labs(x = "mean temp (°C)")
)

p$p1 + p$p2 + p$p3 +
  plot_layout(axes = "collect", guides = "collect",
              widths = c(1, 1.5, 2)) &
  theme(legend.position = "bottom")

```



## dev trajectories

```{r}
# plots avgs; incls pmds
df <- dfs_tidy$long %>%
  filter(#is.sup != 1 # or just NA this column if dgaf
         ) %>%
  group_by(is.sup) %>%
  CalcDevSS() %>%
  filter(trt.type == "dev",
         instar != "LPI",
         !is.na(is.sup) # is.na(is.sup) = things that died < 5
         ) %>%
  mutate(instar = factor(instar, levels = c("pmd", "hatch", "2nd", "3rd", "4th", "5th", "6th", "wander", "pupa", "eclose"))) %>%
  filter(!(instar %in% c("hatch", "pmd", "2nd")))

.plotfn <- function(x){
  x %>%
    filter(!(instar %in% c("wander", "pupa", "eclose"))) %>%
    ggplot(aes(#col = trt.maxT, 
               col = trt.meanT,
               lty = trt.flucT,
             group = interaction(trt.meanT, trt.flucT))) +
    geom_point(#aes(alpha = n),
               size = 2.5) +
  geom_line() +
  scale_color_hue(direction = -1) +
  theme_bw() +
    facet_wrap(~is.sup, labeller = as_labeller(c(`0` = "non-supernumerary",
                                                 `1` = "supernumerary")),
               scales = "free_x") +
    labs(lty = "fluctuation", col = "mean temp") +
    scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE))
}

# dev trajectory
df %>%
  .plotfn() +
  aes(y = avg.logmass, x = avg.tt,
      shape = instar) +
  geom_errorbar(aes(ymax = avg.logmass + se.logmass,
                    ymin = avg.logmass - se.logmass),
                width = 0.2, lty = "solid", show.legend = FALSE) +
  geom_errorbarh(aes(xmax = avg.tt + se.tt,
                     xmin = avg.tt - se.tt),
                 height = 0.1, lty = "solid", show.legend = FALSE) +
  labs(y = "ln mass", x = "time to instar (days)",
       shape= "instar")


# mass vs instar
df %>%
  .plotfn() +
  aes(y = avg.logmass, x = instar,
      shape = trt.maxT) +
  geom_errorbar(aes(ymax = avg.logmass + se.logmass,
                    ymin = avg.logmass - se.logmass),
                width = 0.1, lty = "solid", show.legend = FALSE) +
    labs(y = "ln mass", x = "instar",
       shape= "max temp")

# development rate vs instar
df %>%
  .plotfn() +
  aes(y = avg.tt, x = instar,
      shape = trt.maxT) +
  geom_errorbar(aes(ymax = avg.tt + se.tt,
                    ymin = avg.tt - se.tt),
                width = 0.1, lty = "solid", show.legend = FALSE) +
  labs(y = "time (days)", x = "instar", shape = "max temp")
```

```



# tdt stuff

```{r}
# df prep
df <- dfs_tidy$wide %>%
  CalcTDTSS()
```

## combined mass/time
```{r}
df %>%
  filter(instar == "24h") %>%
  ggplot(aes(x = avg.dmass, y = avg.exit,
             #lty = cohort,
             col = trt.maxT, shape = trt.flucT)) +
  geom_point(size = 2) +
  geom_line() +
  geom_errorbar(aes(ymax = avg.exit + se.exit,
                    ymin = avg.exit - se.exit),
                width = 5) +
  # geom_errorbarh(aes(xmax = avg.dmass + se.dmass,
  #                    xmin = avg.dmass - se.dmass)) +
  scale_color_hue(direction = -1) +
  theme_bw() +
  labs(y = "days survived after transferring",
       x = "mass diff. 24h after transferring",
       col = p_scales$lab_maxT,
       shape = p_scales$lab_flucT)
```

## exit time
```{r}
# one fig
df %>%
  #filter(instar == "24h") %>%
  ggplot(aes(y = avg.exit, x = trt.maxT,
             #x = trt.meanT, shape = trt.maxT,
             #col = trt.flucT, 
              group = interaction(trt.flucT),
             )) +
  #facet_wrap(~cohort) +
  geom_line(aes(lty = trt.flucT,)) +
  geom_errorbar(aes(ymax = avg.exit + se.exit,
                    ymin = avg.exit - se.exit),
                width = 0.25, lty = "solid", show.legend = FALSE
                ) +
  geom_point(aes(col = trt.meanT, 
                 shape = trt.meanT),
             size = 2.5) +
  #scale_color_hue(direction = -1) +
  #scale_color_brewer(palette = "Reds") +
   scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
  theme_bw() +
  labs(y = "days survived after transfer to 40°C",
       x = "maximum temperature (°C)",
       #col = p_scales$lab_flucT,
       col = "mean temp",
       shape = "mean temperature (°C)",
       lty = p_scales$lab_flucT)
```

```{r}
.plotfn <- function(x){
  x %>%
    filter(trt.type == "tdt",
           instar == "0h" # drop dups
           ) %>%
    ggplot(aes(y = avg.exit, 
               shape = trt.maxT, fill = trt.flucT,
               lty = trt.flucT, #color = trt.meanT,
               group = trt.flucT,)) +
    geom_point(size = 2) +
    #geom_line() +
    geom_errorbar(aes(ymax = avg.exit + se.exit,
                    ymin = avg.exit - se.exit),
                  width = 0.25, lty = "solid", show.legend = FALSE) +
    geom_text(aes(label = n),
              vjust = -0.2, hjust = -0.3,
              show.legend = FALSE) +
    scale_shape_manual(values = c(`33` = 21, `40` = 24)) +
    scale_fill_manual(values = c(`3.5` = "white", `7` = "black")) +
    guides(shape = guide_legend(override.aes = list(shape = c(16, 17))),
           fill = guide_legend(override.aes = list(shape = c(1, 16)))) +
    #scale_color_manual(values = hcl.colors(4, "Roma", rev = TRUE)) +
    labs(y = "days to exit (from transfer)",
         #lty = "fluctuation (°C)",
         shape = "max temp",
         fill = "fluct temp",
        # color = "mean temp"
    ) +
    theme_bw()
}

p <- list(
  p1 = df %>%
    .plotfn() +
    aes(x = trt.maxT) +
    labs(x = "max temp (°C)"),
  
  p2 = df %>%
    .plotfn() +
    aes(x = trt.minT) +
    labs(x = "min temp (°C)"),
  
  
  p3 = df %>%
    .plotfn() +
    aes(x = trt.meanT) +
    labs(x = "mean temp (°C)")
)

p$p1 + p$p2 + p$p3 +
  plot_layout(axes = "collect", guides = "collect",
              widths = c(1, 1.5, 2)) &
  theme(legend.position = "bottom")
```



## mass change

```{r}
.plotfn <- function(x){
  x %>%
    filter(instar != "0h") %>%
    ggplot(aes(x = trt.maxT,
               #x = trt.meanT, shape = trt.maxT,
               col = trt.flucT, lty = trt.flucT, #shape = trt.flucT,
               shape = trt.meanT,
               group = trt.flucT)) +
    geom_point(size = 2) +
    geom_line() +
    #facet_wrap(~cohort) +
    scale_color_hue(direction = -1) +
    theme_bw() +
    labs(x = "maximum temperature (°C)",
         col = p_scales$lab_flucT,
         lty = p_scales$lab_flucT,
         shape = "mean temperature (°C)"
         #shape = p_scales$lab_flucT
    ) +
    guides(shape = guide_legend(override.aes = list(color = c("#F8766D", "#00BFC4", "#F8766D", "#00BFC4"))))
}

# 2x2 by transfer day
df %>%
  .plotfn() +
  aes(y = avg.dmass) +
  geom_errorbar(aes(ymax = avg.dmass + se.dmass,
                    ymin = avg.dmass - se.dmass),
                width = 0.25, lty = "solid", show.legend = FALSE
  ) +
  facet_wrap(~instar, labeller = as_labeller(c(`24h` =  "24h after transfer to 40°C",
                                               `48h` =  "48h after transfer to 40°C"))) +
  labs(y = "mass difference (mg)")
  


df %>%
  .plotfn() +
  aes(y = avg.rmass) +
  geom_errorbar(aes(ymax = avg.rmass + se.rmass,
                    ymin = avg.rmass - se.rmass),
                width = 0.25, lty = "solid", show.legend = FALSE
                ) +
  facet_wrap(~instar, labeller = as_labeller(c(`24h` =  "24h:0h after transfer to 40°C",
                                               `48h` =  "48h:24h after transfer to 40°C"))) +
  labs(y = "mass ratio")
```

```{r}
.plotfn <- function(x){
  x %>%
    filter(instar %in% c("24h", "48h")) %>%
    ggplot(aes(x = instar,
               #shape = trt.maxT, 
               shape = trt.meanT,
               col = trt.maxT, 
               lty = trt.flucT, 
               group = interaction(trt.flucT, trt.maxT))) +
    geom_point(size = 2) +
    geom_line() +
    scale_color_hue(direction = -1) +
    theme_bw() +
    labs(#col = "fluctuation", lty = "fluctuation",
      #shape = "max temp",
      #shape = p_scales$lab_maxT,
      shape = "mean temperature (°C)",
      col = p_scales$lab_maxT,
      lty = p_scales$lab_flucT
    )
}

# 0:24 vs 24:48
df %>%
  .plotfn() +
  aes(y = avg.dmass) +
  geom_errorbar(aes(ymax = avg.dmass + se.dmass,
                    ymin = avg.dmass - se.dmass),
                width = 0.25, lty = "solid", show.legend = FALSE
                ) +
  labs(y = "change in mass (mg)",
       x = "h after transfer to 40°C",)

df %>%
  .plotfn() +
  aes(y = avg.rmass) +
  geom_errorbar(aes(ymax = avg.rmass + se.rmass,
                    ymin = avg.rmass - se.rmass),
                width = 0.25, lty = "solid", show.legend = FALSE
                )
```


